---
title: "Foo Factors"
author: "Melissa Armstrong"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Foo Factors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Vignette Info

I don't have much to say but I'll try to pull stuff out of examples or tests or something:

Binding two factors with fbind():

```{r}
library(foofactors)
(a <- factor(c("character", "hits", "your", "eyeballs")))
(b <- factor(c("but", "integer", "where it", "counts")))
```

Concatenating is weird:

```{r}
c(a, b)
```

So fbind() glues two factors together and returns a factor:

```{r}
fbind(a, b)
```

Sometimes we want a table of frequencies for the levels of a factor. Base table() returns an object of class table, which can be inconvenient for downstream work. Processing as.data.fram() can help but it's still clunky:

```{r}
set.seed(1234)
x <- factor(sample(letters[1:5], size = 100, replace = TRUE))
table(x)
as.data.frame(table(x))
```

The freq_out() function returns a frequency table as a well-named tbl_df:

```{r}
freq_out(x)
```
